---
title: "Test_therMizer_temperature"
author: "Phoebe.Woodworth-Jefcoats@noaa.gov"
date: "8/17/2020"
output:
  html_document:
    toc: yes
    fig_width: 10
    fig_height: 5
---

## Purpose

The purpose of this script is to test ther therMizer extension for FishMIP using only temperature and fishing input.  This is so that the mizer resource spectra and feeding levels can be examined and the CMIP6 plankton forcing scaled appropriately (if necessary).

## Load libraries
Mizer 2.0.3 or later version is needed to use the extension. 

```{r message = FALSE, warning = FALSE}
library(mizer)
```

## Set up multispecies model 
For the FishMIP simulations, we'll be using the species parameters in [Woodworth-Jefcoats et al. 2019](https://www.frontiersin.org/articles/10.3389/fmars.2019.00383/full).  We'll also follow their implemetation of fishing mortality, so will need to create a selectivity function which we'll call `knife_edge_phased`.

```{r message = FALSE, warning = FALSE}

# Create the selectivity function:

#' Size based knife-edge selectivity function that is phased in 
#'
#' A knife-edge selectivity function where only sizes greater or equal to
#' \code{knife_edge_size1} are selected.  Selectivity is then phased in through
#' size \code{knife_edge_size2}.  This simulates the reduced effectiveness of 
#' longline gear for smaller fish
#'
#' @param w The size of the individual.
#' @param knife_edge_size1 The size at which the knife-edge is initiated.
#' @param knife_edge_size2 The size at which selectivity is fully realized.
#' @export
knife_edge_phased <- function(w, knife_edge_size1, knife_edge_size2, ...) { 
	sel <- rep(0, length(w)) 
	
	# Phased in linearly
	F0 <- which(w < knife_edge_size1) # to find one size smaller than that fished, for the 0 value 
	F1 <- which(w < knife_edge_size2) # to find end of escalation size range 
	lo_sel <- max(F0):max(F1) 
	sel[lo_sel] <- seq(0, 1, length = length(lo_sel)) # linear increase from 0 to F 
	sel[w >= knife_edge_size2] <- 1 
	return(sel) 
	
} 

# Load species parameters
species_params <- read.csv('NPac_species_params.csv')

# Load interaction matrix
inter <- read.csv('inter_NPAC.csv', row.names = 1)
inter <- as(inter, "matrix")

# Create the params object
params <- newMultispeciesParams(species_params, interaction = inter, min_w_pp = 1e-14, no_w = 100, kappa = 1e12, w_pp_cutoff = 455400*1.1)

# Run a projection to make sure the selectivity function is working
sim <- project(params, t_max = 500, effort = 0.1)
plot(sim)

```

Excellent!  Things are working.  Let's test the FishMIP fishing scenarios:  

* nat: no fishing (naturalized run, 1950 - 2100)  
* histsoc: varying direct human influences in the historical period (1950-2014) (i.e., historical estimates of fishing effort)  
* 2015soc: fixed year-2015 direct human influences (2015 - 2100) (i.e., fishing effort)  

Note that the histsoc and 2015soc scenarios will be concatonated.

## Test FishMIP fishing scenarios, without climate data

In this section, we'll test the two FishMIP fishing scenarios.  The time series of fishing mortality, "FishingEffort.dat" was created with "CreateF.Rmd".  We're also going to create another time series with F = 0 so that we can use the same years for all our scenarios.  This makes incorporating the temperature functions easier later on because all the time values will agree.

```{r message = FALSE, warning = FALSE}

# Load fishing scenario
effort_Fvar <- read.table("FishingEffort.dat", sep = " ")
effort_Fvar <- effort_Fvar[,2] # Column 1 = year, which we won't need
effort_Fvar <- as(effort_Fvar, "matrix")

# Build fishing effort arrays
# Since we're following the approach of Woodworth-Jefcoats et al. 2019, we'll begin the model with 600 years of constant input for spinup.  This means the first year will be 1350 (1950 - 600).
times <- seq(1350, 2100, by = 1)
gear_names <- c("Longline")
effort_array_Fvar <- array(NA, dim = c(length(times), length(gear_names)), dimnames = list(time = times, gear = gear_names))
effort_array_F0 <- array(NA, dim = c(length(times), length(gear_names)), dimnames = list(time = times, gear = gear_names))

# Now fill the array
# Remember, the first 600 years are for spin-up.
# During this time, the first input value is repeated at each time step.
for (t in (times-1349)){
	if (t <= 601){ 
		effort_array_Fvar[t,"Longline"] <- effort_Fvar[1]
		effort_array_F0[t,"Longline"] <- 0
	} else {
		effort_array_Fvar[t,"Longline"] <- effort_Fvar[t-600]
		effort_array_F0[t,"Longline"] <- 0
		}
}

# Run two simulations:
# No effort
# FishMIP effort
sim_F0 <- project(params, t_max = length(times), effort = effort_array_F0)
plot(sim_F0)

sim_Fonly <- project(params, t_max = length(times), effort = effort_array_Fvar)
plot(sim_Fonly)

```

That looks good.  Now we can move to incorporating temperature.

## Load temperature data

Before we crate the temperature functions, we'll load in the FishMIP temperature forcing.  
There are four climate scenarios:  

* picontrol: pre-industrial climate as simulated by the Earth System Models (ESMs)  
* historical: historical climate as simulated by the ESMs, starting in 1950  
* ssp126: SSP1-RCP2.6 climate as simulated by the ESMs  
* ssp585" SSP5-RCP8.5 climate as simulated by the ESMs  

and both ssp126 and ssp585 will be appended to historical.  Note that only the years 1950 - 2100 are needed.  These were created with "PrepTemperature_GFDL.Rmd" and "PrepTemperature_IPSL.Rmd".  

```{r message = FALSE, warning = FALSE}

# Load data for each CMIP6 model: GFDL-ESM4 and IPSL-CM6A-LR
GFDL_temperature_PIcontrol <- read.table("GFDL_ocean_temp_array_PIcontrol.dat")
GFDL_temperature_CC126 <- read.table("GFDL_ocean_temp_array_CCscenario_126.dat")
GFDL_temperature_CC585 <- read.table("GFDL_ocean_temp_array_CCscenario_585.dat")

IPSL_temperature_PIcontrol <- read.table("IPSL_ocean_temp_array_PIcontrol.dat")
IPSL_temperature_CC126 <- read.table("IPSL_ocean_temp_array_CCscenario_126.dat")
IPSL_temperature_CC585 <- read.table("IPSL_ocean_temp_array_CCscenario_585.dat")

GFDL_temperature_PIcontrol <- as(GFDL_temperature_PIcontrol, "matrix")
GFDL_temperature_CC126 <- as(GFDL_temperature_CC126, "matrix")
GFDL_temperature_CC585 <- as(GFDL_temperature_CC585, "matrix")

IPSL_temperature_PIcontrol <- as(IPSL_temperature_PIcontrol, "matrix")
IPSL_temperature_CC126 <- as(IPSL_temperature_CC126, "matrix")
IPSL_temperature_CC585 <- as(IPSL_temperature_CC585, "matrix")

# Build temperature arrays following methods used above
species <- params@species_params$species
ocean_temp_array_GFDL_PIcontrol <- array(NA, dim = c(length(times), length(species)), dimnames = list(time = times, sp = species))
ocean_temp_array_GFDL_CC126 <- array(NA, dim = c(length(times), length(species)), dimnames = list(time = times, sp = species))
ocean_temp_array_GFDL_CC585 <- array(NA, dim = c(length(times), length(species)), dimnames = list(time = times, sp = species))
ocean_temp_array_IPSL_PIcontrol <- array(NA, dim = c(length(times), length(species)), dimnames = list(time = times, sp = species))
ocean_temp_array_IPSL_CC126 <- array(NA, dim = c(length(times), length(species)), dimnames = list(time = times, sp = species))
ocean_temp_array_IPSL_CC585 <- array(NA, dim = c(length(times), length(species)), dimnames = list(time = times, sp = species))

for (t in (times-1349)){
	if (t <= 601){ 
		ocean_temp_array_GFDL_PIcontrol[t,] <- GFDL_temperature_PIcontrol[1,]
		ocean_temp_array_GFDL_CC126[t,] <- GFDL_temperature_CC126[1,]
		ocean_temp_array_GFDL_CC585[t,] <- GFDL_temperature_CC585[1,]
		ocean_temp_array_IPSL_PIcontrol[t,] <- IPSL_temperature_PIcontrol[1,]
		ocean_temp_array_IPSL_CC126[t,] <- IPSL_temperature_CC126[1,]
		ocean_temp_array_IPSL_CC585[t,] <- IPSL_temperature_CC585[1,]
	} else {
		ocean_temp_array_GFDL_PIcontrol[t,] <- GFDL_temperature_PIcontrol[t-600,]
		ocean_temp_array_GFDL_CC126[t,] <- GFDL_temperature_CC126[t-600,]
		ocean_temp_array_GFDL_CC585[t,] <- GFDL_temperature_CC585[t-600,]
		ocean_temp_array_IPSL_PIcontrol[t,] <- IPSL_temperature_PIcontrol[t-600,]
		ocean_temp_array_IPSL_CC126[t,] <- IPSL_temperature_CC126[t-600,]
		ocean_temp_array_IPSL_CC585[t,] <- IPSL_temperature_CC585[t-600,]
		}
}

```

## Create the parameters that are derived from user-input parameters

To scale the effect of temperature on encounter rate to a value ranging from 0 - 1, it is necessary to divide by the maximum possible value for each species.  To scale the effect of temperature on metabolism to a value ranging from 0 - 1, it is necessary to subtract the minimum vaule for each species and then divide by the range.  This requires a bit of straightforward arithmetic, and users could do this on their end if they're so inclined.  These parameters handle that math so the user doesn't have to.

We're also going to create a parameter called `t_idx` that will help with the simulations.  This parameter will provide the correct time index for temperature during the simulations.

```{r message = FALSE, warning = FALSE}

params@species_params$encounter_scale <- rep(NA, length(params@species_params$temp_min))

for (indv in seq(1:length(params@species_params$temp_min))){
  
  # Create a vector of all temperatures each species might encounter
  temperature <- seq(params@species_params$temp_min[indv], params@species_params$temp_max[indv], by=0.1)
  
  # Find the maximum value of the unscaled effect of temperature on encounter rate for each species 
  params@species_params$encounter_scale[indv] <- max((temperature) * (temperature - params@species_params$temp_min[indv]) * (params@species_params$temp_max[indv] - temperature))
}

# Determine the minimum, maximum, and range of value for the effect of temperature on metabolism
min_metab_value <- (exp(25.22 - (0.63/((8.62e-5)*(273+params@species_params$temp_min)))))
max_metab_value <- (exp(25.22 - (0.63/((8.62e-5)*(273+params@species_params$temp_max)))))
		
params@species_params$metab_min <- min_metab_value
params@species_params$metab_range <- max_metab_value - min_metab_value
		
# Time indexing parameter
# This will be added to t to convert the year into an index for the ocean_temp array
if (min(times) == 0) {
  other_params(params)$t_idx = 1
} else if (min(times) == 1) {
  other_params(params)$t_idx = 0
} else {
  other_params(params)$t_idx = -(min(times) - 1)
}
  
		
```

## Create the new rate functions

Temperature will be added to the fuctions to determine encounter rate and energy available for growth and reproduction.

To scale encounter rate with temperature, we're essentially taking a temperature-dependent proportion of the value calculated by the mizerEncounter function.  If species are at their thermal optimum, we take the full value.  Elsewhere in their thermal range, we take a proportion that goes to zero at the limits of species' thermal tolerence.  

```{r message = FALSE, warning = FALSE}

therMizerEncounter <- function(params, n, n_pp, n_other, t, ...) {
      
      # Access the correct element
      temp_at_t <- params@other_params$other$ocean_temp[t + params@other_params$other$t_idx,]
      
      # Calculate unscaled temperature effect using a generic polynomial rate equation
      unscaled_temp_effect <- temp_at_t * (temp_at_t - params@species_params$temp_min) * (params@species_params$temp_max - temp_at_t)
      
      # Scale using new parameter
      scaled_temp_effect <- unscaled_temp_effect / params@species_params$encounter_scale
      
      # Set the encounter rate to zero if temperature is outside species' thermal tolerance
      above_max <- which(temp_at_t > params@species_params$temp_max)
      below_min <- which(temp_at_t < params@species_params$temp_min)
      
      if(length(above_max) > 0)
        scaled_temp_effect[above_max] = 0
      
      if(length(below_min) > 0)
        scaled_temp_effect[below_min] = 0
      
      # Calculate maximum possible encounter rate
      max_encounter <- mizerEncounter(params, n = n, n_pp = n_pp, n_other = n_other, ...)
      
      # Apply temperature effect
      # return(sweep(max_encounter, 1, scaled_temp_effect, '*', check.margin = FALSE))
      return(max_encounter*scaled_temp_effect)
      
}

```

To calculate the effect of temperature on metabolim, we use an Arrhenius function to scale the cost of metabolism.  When species are at their thermal maximum, the cost of metabolism is at its maximum.  When species are at their thermal minimum, the cost of metabolism is at its minimum

```{r message = FALSE, warning = FALSE}

therMizerEReproAndGrowth <- function(params, n, n_pp, n_other, t, encounter,
                                 feeding_level, ...) {
    
    # Access the correct element
    temp_at_t <- params@other_params$other$ocean_temp[t + params@other_params$other$t_idx,]
    
    # Arrhenius equation
    unscaled_temp_effect <- (exp(25.22 - (0.63/((8.62e-5)*(273+temp_at_t)))))
      
    # Arrhenius equation scaled to a value between 0 and 1
		temp_effect_metabolism <- (unscaled_temp_effect - params@species_params$metab_min) / params@species_params$metab_range
		
		# Set the EReproAndGrowth to zero if temperature is outside species' thermal tolerance
    Emultiplier <- rep(1, length(params@species_params$species))
		
		above_max <- which(temp_at_t > params@species_params$temp_max)
    below_min <- which(temp_at_t < params@species_params$temp_min)
    
    if(length(above_max) > 0)
      Emultiplier[above_max] = 0
    
    if(length(below_min) > 0)
      Emultiplier[below_min] = 0
  
		# Apply scaled Arrhenius value to metabolism
    (sweep((1 - feeding_level) * encounter, 1,
               params@species_params$alpha, "*", check.margin = FALSE) - 
      params@metab*temp_effect_metabolism)*Emultiplier  
      
}

```

## Update the functions

Replacing mizer's `Encounter` and `EReproAndGrowth` functions with the therMizer extension functions

```{r message = FALSE, warning = FALSE}

params <- setRateFunction(params, "Encounter", "therMizerEncounter")
params <- setRateFunction(params, "EReproAndGrowth", "therMizerEReproAndGrowth")

```

## Run the simulations

Because temperature is a parameter, we'll need to make unique `params` objects for each model and climate scenarios.  This means we'll have six new `params` objects (2 models x 3 climate scenarios).

```{r message = FALSE, warning = FALSE}

# Create parameter objects
params_GFDL_PI <- params
params_GFDL_CC126 <- params
params_GFDL_CC585 <- params

params_IPSL_PI <- params
params_IPSL_CC126 <- params
params_IPSL_CC585 <- params

# Attach temperature
other_params(params_GFDL_PI)$ocean_temp <- ocean_temp_array_GFDL_PIcontrol
other_params(params_GFDL_CC126)$ocean_temp <- ocean_temp_array_GFDL_CC126
other_params(params_GFDL_CC585)$ocean_temp <- ocean_temp_array_GFDL_CC585

other_params(params_IPSL_PI)$ocean_temp <- ocean_temp_array_IPSL_PIcontrol
other_params(params_IPSL_CC126)$ocean_temp <- ocean_temp_array_IPSL_CC126
other_params(params_IPSL_CC585)$ocean_temp <- ocean_temp_array_IPSL_CC585

```

Now we can run the simulations.  There are 12 runs here: 3 climate scenarios x 2 fishing scenarios x 2 CMIP6 models.

```{r message = FALSE, warning = FALSE}
sim_GFDL_PI_F0 <- project(params_GFDL_PI, t_max = length(times), effort = effort_array_F0)
sim_GFDL_CC126_F0 <- project(params_GFDL_CC126, t_max = length(times), effort = effort_array_F0)
sim_GFDL_CC585_F0 <- project(params_GFDL_CC585, t_max = length(times), effort = effort_array_F0)

sim_IPSL_PI_F0 <- project(params_IPSL_PI, t_max = length(times), effort = effort_array_F0)
sim_IPSL_CC126_F0 <- project(params_IPSL_CC126, t_max = length(times), effort = effort_array_F0)
sim_IPSL_CC585_F0 <- project(params_IPSL_CC585, t_max = length(times), effort = effort_array_F0)

sim_GFDL_PI_Fvar <- project(params_GFDL_PI, t_max = length(times), effort = effort_array_Fvar)
sim_GFDL_CC126_Fvar <- project(params_GFDL_CC126, t_max = length(times), effort = effort_array_Fvar)
sim_GFDL_CC585_Fvar <- project(params_GFDL_CC585, t_max = length(times), effort = effort_array_Fvar)

sim_IPSL_PI_Fvar <- project(params_IPSL_PI, t_max = length(times), effort = effort_array_Fvar)
sim_IPSL_CC126_Fvar <- project(params_IPSL_CC126, t_max = length(times), effort = effort_array_Fvar)
sim_IPSL_CC585_Fvar <- project(params_IPSL_CC585, t_max = length(times), effort = effort_array_Fvar)

```

Take a look at plots for each scenario.

```{r message = FALSE, warning  = FALSE}

plot(sim_GFDL_PI_F0)
plot(sim_GFDL_CC126_F0)
plot(sim_GFDL_CC585_F0)
plot(sim_IPSL_PI_F0)
plot(sim_IPSL_CC126_F0)
plot(sim_IPSL_CC585_F0)
plot(sim_GFDL_PI_Fvar)
plot(sim_GFDL_CC126_Fvar)
plot(sim_GFDL_CC585_Fvar)
plot(sim_IPSL_PI_Fvar)
plot(sim_IPSL_CC126_Fvar)
plot(sim_IPSL_CC585_Fvar)

```

